---
title: "get-members"
author: "John D. Smith"
date: "December 22, 2015"
output: html_document
---
&category=34,2

tech category=34
careerbiz - category=2

only=id,name
offset = 0-?

API docoumentation: 
* groups: http://www.meetup.com/meetup_api/docs/find/groups/ 
* members: http://www.meetup.com/meetup_api/docs/2/members/
for testing: https://secure.meetup.com/meetup_api/console/?path=/find/groups

```{r}
library(httr)
library(stringr)
library(lubridate)
library(jsonlite)
library(plyr)
library(dplyr)
library(tidyjson)
library(readr)
library(ggplot2)
source("~/Rfunctions/setup_my_google.R")
setwd("~/Documents/cch/data-sci-pdx")
options(stringsAsFactors = FALSE)

# group_id <- 16967362
meetup_api <- Sys.getenv("meetup_api")

```
Standard tidyjson functions
```{r}
my_spread_values <- function(x, names_list, string_type) { 
  # A wrapper for "spread_values" that taks a list of names and a string type, so there's much less code...
  # stopifnot( as.character(string_type) %in% c("jnumber", "jstring", "jlogical") )
  do.call("spread_values", 
    c(list(x), setNames(lapply(names_list, string_type), as.list(names_list) ) ) )
} 

get_json_tbl_data_types <- function(my_tbl_json) {
# find the keys to the json, to determine which function sequence to use for retrieval
  json_data_types <- my_tbl_json %>% gather_array %>% gather_keys %>% json_types %>% group_by(key, type) %>% summarise(count = n())
  json_data_types <- ungroup(json_data_types) %>% mutate(key = as.character(key), type = as.character(type)) %>% arrange(type, key)
}

get_object_keys <- function(json_obj, object_name) {
# slightly different sequence to find the keys to an OBJECT:
  json_obj %>% gather_array %>%
  enter_object(object_name) %>% gather_keys %>% json_types %>% 
  group_by(key, type) %>% summarise(count = n())
}

```
identify groups
```{r}
groups <- readRDS( "meetup_groups.Rdata")

# for testing:
groups %>% filter(grepl("data|chifoo", name, ignore.case = T)) %>% select(id,name)
```

explore the json about get member info ... 
separate query to get members other groups...
```{r}

get_json_tbl <- function(num_members, page_num, group_id, meetup_api = Sys.getenv("meetup_api")) {
 
  
  (url <- paste0(url_member_stub,url_num_of_groups,url_query,group_id,url_page))
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)
  }

json <- get_json_tbl(num_members = 200 , group_id = 16967362, page_num = 1)

# json2 <- get_json_tbl(num_members = 200, page_num = 1)
# json3 <- get_json_tbl(num_members = 200, page_num = 2)

json_obj <- json %>% as.tbl_json 

json_data_types <- get_json_tbl_data_types(json_obj)

json_data_types %>% filter(type == "number") %>% select(key) %>% unlist %>% as.array
json_data_types %>% filter(type == "string") %>% select(key) %>% unlist %>% as.array 
json_data_types %>% filter(type != "string" & type != "number") %>% select(key, type) 

num_list <- c("id", "joined", "lat", "lon", "visited")
chr_list <- c("bio", "city", "country", "hometown", "lang", "link", "name", "state", "status")

other_services_keys <- get_object_keys(json_obj, "other_services")
other_services_keys

service_key_list <- c("flickr", "tumblr", "twitter", "linkedin")

```

# Now define functions to upack json for this query
```{r}
get_json_tbl <- function(page_num, group_id) {
	url <- paste0("https://api.meetup.com/2/members?sign=true&page=200&key=", meetup_api, "&group_id=", group_id, "&offset=", page_num)
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)  %>% as.tbl_json 
  }

get_group_data_frame <- function(group_id) {
  
  page_num <- 0  
  num_list <- c("joined", "lat", "lon", "visited")
  chr_list <- c("id", "bio", "city", "country", "hometown", 
  	"lang", "link", "name", "state", "status")
  
  while (page_num >= 0) {
    
    tbl_json <- get_json_tbl(page_num = page_num, group_id = group_id)
  
  	 mem_strings <- tbl_json %>% gather_array %>% 
  	   my_spread_values(
  	      chr_list, jstring ) %>% 
  	   select(-document.id, rec_num = array.index) %>% 
  	   mutate(member_of_group = group_id)
  
  	 mem_numerics <- tbl_json %>% gather_array %>% 
  	   my_spread_values(
  	      num_list, jnumber ) %>% 
  	    select(-document.id, rec_num = array.index) 
  	 mem_numerics$joined <- as.POSIXct(mem_numerics$joined/1000, origin = "1970-01-01")
  	 mem_numerics$visited <- as.POSIXct(mem_numerics$visited/1000, origin = "1970-01-01")
      
  	 mem_twitter_id <- tbl_json %>% gather_array %>% 
  	   spread_values(mem_id = jstring("id") ) %>%
  	   enter_object("other_services") %>% enter_object("twitter") %>% 
  	   spread_values(twitter_id = jstring("identifier") ) %>% select(-array.index, -document.id)   
  
  	 mem_linkedin_id <- tbl_json %>% gather_array %>% 
  	   spread_values(mem_id = jstring("id") ) %>%
  	   enter_object("other_services") %>% enter_object("linkedin") %>% 
  	   spread_values(linkedin_id = jstring("identifier") ) %>% 
  	   select(-array.index, -document.id)   
           
      members <- left_join(mem_strings, mem_numerics, by = c("rec_num" = "rec_num"))
      members <- left_join(members, mem_twitter_id, by = c("id" = "mem_id")) 
      members <- left_join(members, mem_linkedin_id, by = c("id" = "mem_id")) %>% 
        select(-rec_num)    
      
     member_topics <- tbl_json %>% gather_array %>% 
       spread_values(member_id = jstring("id")) %>%
       enter_object("topics") %>% gather_array %>%
       my_spread_values(c("id","name","urlkey"), jstring) %>% 
       select(-array.index, -document.id) %>% 
  	   mutate(member_of_group = group_id) %>% rename(topic_id = id)
    	
      # accumulate batches into groups_id data frames
      if (page_num == 0 ) {
        group_id_members <- members
  	    group_id_topics <- member_topics
  	  } else {
        group_id_members <- bind_rows(group_id_members, members)
        group_id_topics <- bind_rows(group_id_topics, member_topics)
      }
    
      # get another batch or jump out of the retrieval loop
      page_num <- page_num + 1
      if ( dim(mem_strings)[1] < 200 ) { 
        # have run out of data for this group
        page_num <-  -1
      } 
    
    Sys.sleep(1) # wait between iterations
    cat('.')
    
    }  
	
    cat("+")
    return(list("mems" = group_id_members, "topics" = group_id_topics))
  }  # finish this group_id

# test with:
# data_groups_list <-  c("11038292", "16967362", "13789762")

get_many_groups <- function(list_of_ids){
  for (list_num in seq_along(list_of_ids) ) {
    # cat(paste(list_num, ",", list_of_ids[list_num], "\n") )
    dataframes_this_list <- get_group_data_frame(group_id = list_of_ids[list_num])
    # unpack the results
     # accumulate batches into groups_id data frames
      if (list_num == 1 ) {
        # initialize
        cum_members <- dataframes_this_list[["mems"]]
  	    cum_topics <- dataframes_this_list[["topics"]]
  	  } else {
  	    # accumulate
        cum_members <- bind_rows(cum_members, dataframes_this_list[["mems"]])
        cum_topics <- bind_rows(cum_topics, dataframes_this_list[["topics"]])
      }
    }
  return(list("all_members" = cum_members, "all_topics" = cum_topics))  
  }

data_groups_list <- c("11038292", "16967362", "13789762", "18393607", "15174102", "19149214", "17840052", "10136492", "6949282", "17836232", "6622532", "8245962")

many_groups <- get_many_groups(data_groups_list)
more_data_groups_list <- c("19149214", "17753372","16786942")
some_groups <- get_many_groups(more_data_groups_list)
python <- get_many_groups("490808")
useRs <-  get_many_groups("1685557")

```
Extract and save
```{r}
all_members <- many_groups[["all_members"]]
all_topics <- many_groups[["all_topics"]]
more_members <- some_groups[["all_members"]]
more_topics <- some_groups[["all_topics"]]
more_members <- python[["all_members"]]
more_topics <- python[["all_topics"]]
useRs_members <- useRs[["all_members"]]
useRs_topics <- useRs[["all_topics"]]


all_members <- bind_rows(all_members,useRs_members)
all_topics <- bind_rows(all_topics, useRs_topics)

write_rds(all_members, "all_data_meetup_members.Rdata")
write_rds(all_topics, "all_data_meetup_topics.Rdata")

```
retrieve
```{r}
all_members <- readRDS( "all_data_meetup_members.Rdata")
dim(all_members)
all_topics <- readRDS( "all_data_meetup_topics.Rdata")
dim(all_topics)
```
Inpsect and summarize
```{r}
all_members %>% group_by(member_of_group) %>% summarize(member_count = n())
all_members %>% summarize(member_count = n())

group_topics <- all_topics %>% group_by(urlkey) %>% summarize(count = n()) %>% ungroup %>% arrange(desc(count))
dim(group_topics)
# 1486 with "name"
```
topic data munging
```{r}
grouped_topics  <- read_tsv("group_topics_csv.tsv")
View(grouped_topics)
grouped_topics  <- grouped_topics  %>% group_by(url_key_copy)  %>% summarize(count = sum(count))

```
graph em?
* cumulative membership over time by group
* last time visited by group

Start by labeling groups
```{r}
group_tags <- read_tsv("~/Documents/cch/data-sci-pdx/group_tags.tsv", col_types = "cc")
str(group_tags)

all_members <- left_join(all_members, group_tags, by = c("member_of_group" = "ID") )
tag_count  <- all_members %>% group_by(tag) %>% summarise(n_member_count = n()) %>% ungroup %>% arrange(desc(n_member_count))
head(tag_count)
# upload_google_ss(tag_count)
group_members <- all_members %>% filter(member_of_group %in% 
c("11038292", "16967362", "18393607", "1685557", "490808") )
``` 

```{r}
ggplot(all_members, aes(x = tag, y = visited)) + 
  geom_boxplot() +
  ggtitle("Date of last visit, selected Meetup groups") +
  xlab("Group name") +
  ylab("Date of last visit")
# (inherit.aes = stat="identity", position="dodge")
```
Group growth
```{r}
growth <- all_members %>% select(tag,joined) %>% 
  group_by(tag) %>% ungroup 

group_growth <- group_members %>% select(tag,joined) %>% 
  group_by(tag) %>% ungroup 

# %>%  
#    mutate(group_size = row_number)
str(growth)
group_growth <- group_growth %>% ungroup %>% arrange(tag,joined) %>% group_by(tag) %>%  
  mutate(count = 1, head_count =  cumsum(count)) %>% 
  filter(joined > "2012-01-01")
ggplot(group_growth, aes(joined,head_count, colour = tag) ) + geom_line() +
 ggtitle("Membership count by date (withdrawals not included)") +
  xlab("Date joined") +
  ylab("Total members")

```
Wordclouds of member topics
PDX Data Science Group, PDX Data User Group, PDX Data Engineering
R
Python
```{r}
library("wordcloud")
pal <- brewer.pal(6,"Dark2")

main_meetups <- c("11038292", "16967362", "18393607")
r_meetup <- "1685557"
python_meetup <- "490808"

main_meetup_topics <- all_topics %>% filter(member_of_group %in% main_meetups) %>% 
  mutate(topic_name = gsub(" ", "",  name))
# verify the number of topic records
# main_meetup_topics  %>% group_by (member_of_group)  %>% summarize(count = n())

main_meetup_counts <- main_meetup_topics %>% group_by(topic_name) %>% 
  summarize(freq = n()) %>% ungroup
summary(main_meetup_counts$freq)

wordcloud(main_meetup_counts$topic_name,main_meetup_counts$freq, min.freq = 10, max.words = 100, colors = pal)

python_meetup_topics <- all_topics %>% filter(member_of_group == python_meetup) %>% 
  mutate(topic_name = gsub(" ", "",  name))
# verify the number of topic records
# main_meetup_topics  %>% group_by (member_of_group)  %>% summarize(count = n())

python_meetup_counts <- python_meetup_topics %>% group_by(topic_name) %>% 
  summarize(freq = n()) %>% ungroup
summary(python_meetup_counts$freq)

wordcloud(python_meetup_counts$topic_name,python_meetup_counts$freq, min.freq = 10, max.words = 100, colors = pal)

r_meetup_topics <- all_topics %>% filter(member_of_group == r_meetup) %>% 
  mutate(topic_name = gsub(" ", "",  name))
# verify the number of topic records
# main_meetup_topics  %>% group_by (member_of_group)  %>% summarize(count = n())

r_meetup_counts <- r_meetup_topics %>% group_by(topic_name) %>% 
  summarize(freq = n()) %>% ungroup
summary(r_meetup_counts$freq)

wordcloud(r_meetup_counts$topic_name,r_meetup_counts$freq, min.freq = 10, max.words = 100, colors = pal)

```
Get data for Scott Chamberlain
```{r}
r_meetup_members <- all_members %>% filter(member_of_group == r_meetup)
save(r_meetup_topics,r_meetup_members, file="r_members_topics.Rdata")
```

