---
title: "get-meetup-data-api-v3"
author: "John D. Smith"
date: "December 22, 2015"
output: html_document
---
offset = 0-?

API docoumentation: 
* groups: http://www.meetup.com/meetup_api/docs/find/groups/ 
* members: http://www.meetup.com/meetup_api/docs/2/members/
for testing: https://secure.meetup.com/meetup_api/console/?path=/find/groups

Exploring documentation in https://cran.r-project.org/web/packages/tidyjson/vignettes/introduction-to-tidyjson.html

```{r}
library(httr)
library(lubridate)
library(dplyr)
library(tidyjson)
library(readr)
library(magrittr)
library(stringr)
library(ggplot2)

source("~/Rfunctions/setup_my_google.R")
setwd("~/Documents/cch/tidymeetups")
options(stringsAsFactors = FALSE)
meetup_api <- Sys.getenv("meetup_api")
url_stub <- paste0("https://api.meetup.com/find/groups?sign=true&photo-host=public,&page=200,&key=", meetup_api)

```
These functions are common - to parsing json
```{r}

my_spread_values <- function(x, names_list, string_type) { 
  # A wrapper for "spread_values" that taks a list of names and a string type, so there's much less code...
  # stopifnot( as.character(string_type) %in% c("jnumber", "jstring", "jlogical") )
  do.call("spread_values", 
    c(list(x), setNames(lapply(names_list, string_type), as.list(names_list) ) ) )
} 

get_json_tbl_data_types <- function(my_tbl_json) {
# find the keys to the json, to determine which function sequence to use for retrieval
  json_data_types <- my_tbl_json %>% gather_array %>% gather_keys %>% json_types %>% group_by(key, type) %>% summarise(count = n())
  json_data_types <- ungroup(json_data_types) %>% mutate(key = as.character(key), type = as.character(type)) %>% arrange(type, key)
}

get_object_keys <- function(json_obj, object_name) {
# slightly different sequence to find the keys to an OBJECT:
  json_obj %>% gather_array %>%
  enter_object(object_name) %>% gather_keys %>% json_types %>% 
  group_by(key, type) %>% summarise(count = n())
}

```
Groups  data documented here: http://www.meetup.com/meetup_api/docs/find/groups/
&only=created,category,description,id,join_mode,members,name,urlname,visibility,organizer,welcome_message,who,next_event

explore, parse json for a sample to figure out the parsing strategy for the subsequent code
```{r}
get_json_tbl <- function(page_num) {
  # pastes URL together, retrieves json from the api and returns a tbl_json object.
  # url_page <- paste0("&offset=", page_num)
  # url_query <- "&group_id="
  
  url <- paste0(url_stub,"&offset=", page_num)
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)  %>% as.tbl_json 
  }

json1 <- get_json_tbl(page_num = 0)
data_types <- get_json_tbl_data_types(json1)

str_list  <- data_types  %>% filter(type == "string")  %>% select(key)
str_array  <- str_list  %>% unlist  %>% as.array 
str_array

# str_list <- c("city", "country", "description", "join_mode", "link", "name", "state", "timezone", 
# "urlname", "visibility", "who")

num_list  <- data_types  %>% filter(type == "number")  %>% select(key)
num_array  <- num_list  %>% unlist  %>% as.array
num_array
# num_list <- c("created", "id", "lat", "lon", "members", "score" )

data_types %>% filter(type != "string" & type != "number")

cat_keys <- json1 %>% get_object_keys("category") %T>% print
event_keys <- json1 %>% get_object_keys("next_event") %T>% print
org_keys <- json1 %>% get_object_keys("organizer") %T>% print

```


# Now define functions to upack json for this query
```{r}
get_json_tbl <- function(page_num) {
  # pastes URL together, retrieves json from the api and returns a tbl_json object.
  # url_page <- paste0("&offset=", page_num)
  # url_query <- "&group_id="
  
  url <- paste0(url_stub,"&offset=", page_num)
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)  %>% as.tbl_json 
  }

get_group_data_frame <- function() {

  page_num <- 0  
  group_string_vars <- c("score", "id", "name", "link", "urlname", "description",
                         "city", "country", "state", "join_mode", "visibility", 
                         "who", "timezone")
  group_numeric_vars <- c("created", "lat", "lon", "members")

  while (page_num >= 0) {
    
    tbl_json <- get_json_tbl(page_num = page_num)
  
    group_strings <- tbl_json %>% 
        gather_array %>% 
        my_spread_values(
         group_string_vars, jstring ) %>% 
      select(-document.id)
    
    group_numerics <- tbl_json %>% 
        gather_array %>% 
        my_spread_values(
         group_numeric_vars, jnumber )  %>% 
      select(-document.id)
    group_numerics$created <- as.POSIXct(group_numerics$created/1000, origin = "1970-01-01")
    
    group_organizers <- tbl_json %>% 
      gather_array %>% 
      spread_values(group_id = jstring("id" ) ) %>%
      enter_object("organizer") %>%
        spread_values(
            organizer_id = jstring(  "id"),
            organizer_name = jstring("name"),
            organizer_bio = jstring( "bio")
            ) %>% select(-array.index, -document.id )
  
    group_category <- tbl_json %>%  
        gather_array %>%  #gather_keys %>%
        spread_values(group_id = jstring("id" ) ) %>%
          enter_object("category") %>%
          spread_values(
            category_id = jstring("id"),
            category_name = jstring("name"),
            category_short_name = jstring("shortname")
          ) %>% 
       select(-array.index, -document.id )
   
    meet_event <- tbl_json %>%  
      gather_array %>%  #gather_keys %>% 
      spread_values(group_id = jstring("id") ) %>%
        enter_object("next_event") %>% 
        spread_values(
          next_event_id = jstring("id"), 
          next_event_name = jstring("name"), 
          next_event_time = jnumber("time"), 
          next_event_utc_offset = jnumber("utc_offset"), 
          next_event_yes_rsvp_count = jnumber("yes_rsvp_count") 
        ) %>% 
        select(-array.index, -document.id )
      meet_event$next_event_time <- as.POSIXct(meet_event$next_event_time/1000, origin = "1970-01-01")
       
    group <- left_join(group_strings, group_numerics, by = c("array.index" = "array.index"))
    group <- left_join(group, group_organizers, by = c("id" = "group_id")) 
    group <- left_join(group, group_category, by = c("id" = "group_id")) 
    group <- left_join(group, meet_event, by = c("id" = "group_id") ) %>% select(-array.index, -score)
    
    if (page_num == 0 ) {
      groups <- group} else {
      groups <- bind_rows(groups,group)
    }
    
    page_num <- page_num + 1
    if ( dim(group_strings)[1] < 200 ) { 
      page_num <-  -1}
    }
  
  groups
  }

# Unpack, put them together and save...

groups <- get_group_data_frame()

saveRDS(groups, file = "meetup_groups.Rdata")

groups <- readRDS("meetup_groups.Rdata")
```
Dig into tech meetups
```{r}

active_tech <- groups %>% 
  filter(category_name == "Tech")

multi_meetup_organizers <- active_tech %>% group_by(organizer_id) %>% summarise(groups_organized = n()) %>% 
  filter(groups_organized > 1) %>% left_join(active_tech) %>% 
  select(organizer_name, groups_organized, name, link, urlname, description, join_mode, visibility, who, created, members, organizer_bio, next_event_id, next_event_name, next_event_time, next_event_utc_offset, next_event_yes_rsvp_count)

mentions_data <- active_tech %>% filter(str_detect(str_to_lower(active_tech$description),"data")) %>% 
  select(id, name, link, description, join_mode, who, created, members, organizer_name, organizer_bio, next_event_id, next_event_name, next_event_time, next_event_yes_rsvp_count)
dim(mentions_data)
```
Upload to Google Drive.
```{r}
upload_google_ss(mentions_data,"PDX Meetups with 'data' in description")
upload_google_ss(multi_meetup_organizers,"PDX Tech Meetup Organizers with multiple Meetups")
```
Short tags for specific groups
```{r}
group_tags <- read_tsv("~/Documents/cch/tidymeetups/group_tags.tsv", col_types = "cc")
str(group_tags)

```
Retrieve and upload
```{r}
upload_google_ss(groups,"All Portland Meetup groups")
```

```{r}
ggplot(data = groups, aes(category_short_name, members)) + 
  geom_boxplot() + 
  scale_y_log10(breaks = c(0,3,10,30,100,300,1000,3000,10000)) +
  # ylim(NA,5000) +
  coord_flip() +
  # ggtitle("1,262 Portland Meetup Groups") + xlab("Group Category") + ylab("Current number of members (3 groups with more than 5,000 members removed)")
  ggtitle("1,262 Portland Meetup Groups - March 2016") + xlab("Group Category") + ylab("Current number of members")

```

