title: "get-meetup-data-api-v3"
---
author: "John D. Smith"
date: "December 22, 2015"
output: html_document
---
&category=34,2

tech category=34
careerbiz - category=2

only=id,name
offset = 0-?

API docoumentation: 
* groups: http://www.meetup.com/meetup_api/docs/find/groups/ 
* members: http://www.meetup.com/meetup_api/docs/2/members/
for testing: https://secure.meetup.com/meetup_api/console/?path=/find/groups

Exploring documentation in https://cran.r-project.org/web/packages/tidyjson/vignettes/introduction-to-tidyjson.html


```{r}
library(httr)
library(lubridate)
# library(jsonlite)
# library(plyr)
library(dplyr)
library(tidyjson)
library(readr)
library(magrittr)
library(stringr)
# library(rjson)
# library(RJSONIO)
setwd("~/Documents/cch/tidymeetups")
options(stringsAsFactors = FALSE)
meetup_api <- Sys.getenv("meetup_api")
url_stub <- paste0("https://api.meetup.com/find/groups?sign=true&photo-host=public&key=", meetup_api)

get_json <- function(num_groups, page_num) {
  url_num_of_groups <- paste0("&page=",num_groups)
  url_page <- paste0("&offset=", page_num)
  url_query <- "&group_id="
  
  url <- paste0(url_stub,url_num_of_groups,url_query,url_page)
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)  %>% as.tbl_json 
  }

my_spread_values <- function(x, names_list, string_type) { 
  # A wrapper for "spread_values" that taks a list of names and a string type, so there's much less code...
  # stopifnot( as.character(string_type) %in% c("jnumber", "jstring", "jlogical") )
  do.call("spread_values", 
    c(list(x), setNames(lapply(names_list, string_type), as.list(names_list) ) ) )
} 

get_json_data_types <- function(my_tbl_json) {
# find the keys to the json, to determine which function sequence to use for retrieval
  json_data_types <- my_tbl_json %>% gather_array %>% gather_keys %>% json_types %>% group_by(key, type) %>% summarise(count = n())
  json_data_types <- ungroup(json_data_types) %>% mutate(key = as.character(key), type = as.character(type)) %>% arrange(type, key)
}

get_object_keys <- function(json_obj, object_name) {
# slightly different sequence to find the keys to an OBJECT:
  json_obj %>% gather_array %>%
  enter_object(object_name) %>% gather_keys %>% json_types %>% 
  group_by(key, type) %>% summarise(count = n())
}

```
Groups  data documented here: http://www.meetup.com/meetup_api/docs/find/groups/
&only=created,category,description,id,join_mode,members,name,urlname,visibility,organizer,welcome_message,who,next_event
```{r Query API}

json1 <- get_json(num_groups = 200, page_num = 0)
json2 <- get_json(num_groups = 200, page_num = 1)
json3 <- get_json(num_groups = 200, page_num = 2)
json4 <- get_json(num_groups = 200, page_num = 3)
json5 <- get_json(num_groups = 200, page_num = 4)
json6 <- get_json(num_groups = 200, page_num = 5)
json7 <- get_json(num_groups = 200, page_num = 6)

```
explore, parse json for a sample to figure out the subsequent code
```{r}
json1 <- get_json(num_groups = 200, page_num = 0)
data_types <- get_json_data_types(json1)

str_list  <- data_types  %>% filter(type == "string")  %>% select(key)
str_array  <- str_list  %>% unlist  %>% as.array 
str_array

# str_list <- c("city", "country", "description", "join_mode", "link", "name", "state", "timezone", 
# "urlname", "visibility", "who")

num_list  <- data_types  %>% filter(type == "number")  %>% select(key)
num_array  <- num_list  %>% unlist  %>% as.array
num_array
# num_list <- c("created", "id", "lat", "lon", "members", "score" )

data_types %>% filter(type != "string" & type != "number")

cat_keys <- json1 %>% get_object_keys("category") %T>% print
event_keys <- json1 %>% get_object_keys("next_event") %T>% print
org_keys <- json1 %>% get_object_keys("organizer") %T>% print

```


# Now define functions to upack json for this query
```{r}

parse_group <- function(json) {

group_string_vars <- c("score", "id", "name", "link", "urlname", "description", "city", "country", "state", "join_mode", "visibility", "who", "timezone")

group_numeric_vars <- c("created", "lat", "lon", "members")

group1 <- json %>% 
    gather_array %>% 
    my_spread_values(
     group_string_vars, jstring ) %>% 
  select(-document.id)

group2 <- json %>% 
    gather_array %>% 
    my_spread_values(
     group_numeric_vars, jnumber )  %>% 
  select(-document.id)
group2$created <- as.POSIXct(group2$created/1000, origin = "1970-01-01")

group3 <- json %>% 
  gather_array %>% 
  spread_values(group_id = jstring("id" ) ) %>%
  enter_object("organizer") %>%
    spread_values(
        organizer_id = jstring(  "id"),
        organizer_name = jstring("name"),
        organizer_bio = jstring( "bio")
        ) %>% select(-array.index, -document.id )

group_category <- json %>%  
    gather_array %>%  #gather_keys %>%
    spread_values(group_id = jstring("id" ) ) %>%
      enter_object("category") %>%
      spread_values(
        category_id = jstring("id"),
        category_name = jstring("name"),
        category_short_name = jstring("shortname")
      ) %>% 
   select(-array.index, -document.id )
      
group <- left_join(group1, group2, by = c("array.index" = "array.index"))
group <- left_join(group, group3, by = c("id" = "group_id")) 
group <- left_join(group, group_category, by = c("id" = "group_id")) %>% select(-array.index)
group
}

parse_next_event <- function(json) {
  meet_event <- json %>%  as.tbl_json %>% 
  gather_array %>%  #gather_keys %>% 
  spread_values(group_id = jstring("id") ) %>%
    enter_object("next_event") %>% 
    spread_values(
      next_event_id = jstring("id"), 
      next_event_name = jstring("name"), 
      next_event_time = jnumber("time"), 
      next_event_utc_offset = jnumber("utc_offset"), 
      next_event_yes_rsvp_count = jnumber("yes_rsvp_count") 
    ) %>% 
    select(-array.index, -document.id )
    meet_event$next_event_time <- as.POSIXct(meet_event$next_event_time/1000, origin = "1970-01-01")
    meet_event
  }

# Unpack, put them together and save...

group1 <- parse_group(json1)
next_event1 <- parse_next_event(json1)

group2 <- parse_group(json2)
next_event2 <- parse_next_event(json2)

group3 <- parse_group(json3)
next_event3 <- parse_next_event(json3)

group4 <- parse_group(json4)
next_event4 <- parse_next_event(json4)

group5 <- parse_group(json5)
next_event5 <- parse_next_event(json5)

group6 <- parse_group(json6)
next_event6 <- parse_next_event(json6)

group7 <- parse_group(json7)
next_event7 <- parse_next_event(json7)

groups <- bind_rows(group1,group2,group3,group4,group5,group6,group7) 
next_events <- bind_rows(next_event1,next_event2,next_event3,next_event4,next_event5,next_event6,next_event7) 

# already merged into groups, but maybe worth keeping separate

save(groups, next_events, file = "meetup_groups.Rdata")

rm(group1,group2,group3,group4,group5,group6,group7)
rm(next_event1,next_event2,next_event3,next_event4,next_event5,next_event6,next_event7)

```
Dig into tech
```{r}

active_tech <- left_join(groups, next_events, by = c("id" = "group_id") ) %>% 
  filter(category_name == "Tech")

multi_meetup_organizers <- active_tech %>% group_by(organizer_id) %>% summarise(groups_organized = n()) %>% 
  filter(groups_organized > 1) %>% left_join(active_tech) %>% 
  select(organizer_name, groups_organized, name, link, urlname, description, join_mode, visibility, who, created, members, organizer_bio, next_event_id, next_event_name, next_event_time, next_event_utc_offset, next_event_yes_rsvp_count)

have_data <- active_tech %>% filter(str_detect(str_to_lower(active_tech$description),"data")) %>% 
  select(name, link, description, join_mode, who, created, members, organizer_name, organizer_bio, next_event_id, next_event_name, next_event_time, next_event_yes_rsvp_count)
dim(have_data)
```
Upload to Google Drive.
```{r}
upload_google_ss(have_data,"PDX Meetups with 'data' in description")
upload_google_ss(multi_meetup_organizers,"PDX Tech Meetup Organizers with multiple Meetups")
```

