---
title: "get-events"
author: "John D. Smith"
date: "January 28, 2016"
output: html_document
---
&category=34,2

tech category=34
careerbiz - category=2

API docoumentation: 
* http://www.meetup.com/meetup_api/docs/2/events/
* groups: http://www.meetup.com/meetup_api/docs/find/groups/ 
* members: http://www.meetup.com/meetup_api/docs/2/members/

for testing: https://secure.meetup.com/meetup_api/console/?path=/2/events&group_urlname=ny-tech

```{r}
library(httr)
library(stringr)
library(lubridate)
library(jsonlite)
library(plyr)
library(dplyr)
library(tidyjson)
library(readr)
library(ggplot2)
source("~/Rfunctions/setup_my_google.R")
setwd("~/Documents/cch/tidymeetups")
options(stringsAsFactors = FALSE)

# group_id <- 16967362
meetup_api <- Sys.getenv("meetup_api")

```
Standard tidyjson functions
```{r}
my_spread_values <- function(x, names_list, string_type) { 
  # A wrapper for "spread_values" that taks a list of names and a string type, so there's much less code...
  # stopifnot( as.character(string_type) %in% c("jnumber", "jstring", "jlogical") )
  do.call("spread_values", 
    c(list(x), setNames(lapply(names_list, string_type), as.list(names_list) ) ) )
} 

get_json_tbl_data_types <- function(my_tbl_json) {
# find the keys to the json, to determine which function sequence to use for retrieval
  json_data_types <- my_tbl_json %>% gather_array %>% gather_keys %>% json_types %>% group_by(key, type) %>% summarise(count = n())
  json_data_types <- ungroup(json_data_types) %>% mutate(key = as.character(key), type = as.character(type)) %>% arrange(type, key)
}

get_object_keys <- function(json_obj, object_name) {
# slightly different sequence to find the keys to an OBJECT:
  json_obj %>% gather_array %>%
  enter_object(object_name) %>% gather_keys %>% json_types %>% 
  group_by(key, type) %>% summarise(count = n())
}

```
identify groups
```{r}
groups <- readRDS( "meetup_groups.Rdata")

# for testing:
groups %>% filter(grepl("data|chifoo", name, ignore.case = T)) %>% select(id,name)
```

explore the json about get member info ... 
separate query to get members other groups...
```{r}
# https://api.meetup.com/2/events?offset=0&format=json&limited_events=False&group_urlname=ny-tech&photo-host=public&time=-13m%2C1m&page=20&fields=&order=time&status=past&desc=false

url_event_stub <- "https://api.meetup.com/2/events?format=json&limited_events=False&photo-host=public&sign=true&key="
status <- "past"
text_format <- "plain"
time <- "-24m,1m"
offset <- 0
page <- 200
group_id <- "490808"
  
get_json_tbl <- function(page, offset, group_id, meetup_api = Sys.getenv("meetup_api")) {
  
  (url <- paste0(url_event_stub, meetup_api, "&text_format=", text_format, "&status=", status,
                "&time=", time, "&group_id=", group_id, "&page=", page, "&offset=", offset))
  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)  %>% as.tbl_json 
  }

json <- get_json_tbl(group_id = 16967362, offset = 0, page = 200)

# json2 <- get_json_tbl(num_events = 200, page = 1)
# json3 <- get_json_tbl(num_events = 200, page = 2)

json_obj <- json %>% as.tbl_json 

json_data_types <- get_json_tbl_data_types(json_obj)

json_data_types %>% filter(type == "number") %>% select(key) %>% unlist %>% as.array
json_data_types %>% filter(type == "string") %>% select(key) %>% unlist %>% as.array 
json_data_types %>% filter(type != "string" & type != "number") %>% select(key, type) 

get_object_keys(json_obj, "rating")
get_object_keys(json_obj, "group")

```

# Now define functions to upack json for this query and get all events for a specific list of Meetups
```{r}

url_event_stub <- "https://api.meetup.com/2/events?format=json&limited_events=False&photo-host=public&sign=true&key="
status <- "past"
text_format <- "plain"
time <- "-48m,1m"
offset <- 0
page <- 200
# group_id <- "490808"
  
get_json_tbl <- function(page, offset, group_id, meetup_api = Sys.getenv("meetup_api")) {
 
  (url <- paste0(url_event_stub, meetup_api, "&text_format=", text_format, "&status=", status,
                "&time=", time, "&group_id=", group_id, "&page=", page, "&offset=", offset))
  # (url <- paste0(url_event_stub, meetup_api, "&text_format=", text_format, "&status=", status,
  #               "&time=", time, "&group_urlname=pdxpython", "&page=", page, "&offset=", offset))


  raw_contents <- GET(url = url)

  json_raw <- httr::content(raw_contents, type = "text")
  json_contents <- sub('^\\{"results":\\[', "[", json_raw)
  json_contents <- sub('\\],"meta"\\:\\{.*\\}.$', "]",json_contents)
  gsub('\\\\/', "/",json_contents)
  }

# tbl_json <- get_json_tbl(group_id = 16967362, offset = 0, page = 200)

get_event_data_frame <- function(group_id) {
  
  offset <- 0  
  num_list <- c("created", "duration", "headcount", "maybe_rsvp_count", "rsvp_limit", "time", "updated", "utc_offset", "waitlist_count", "yes_rsvp_count")
  chr_list <-  c("description", "event_url", "how_to_find_us", "id", "name", "status", "visibility")

  while (offset >= 0) {
    
    tbl_json <- get_json_tbl(offset = offset, page = 200, group_id = group_id)
  
  	 event_strings <- tbl_json %>% gather_array %>% 
  	   my_spread_values(
  	      chr_list, jstring ) %>% 
  	   select(-document.id, rec_num = array.index) 
  
  	 event_numerics <- tbl_json %>% gather_array %>% 
  	   my_spread_values(
  	      num_list, jnumber ) %>% 
  	    select(-document.id, rec_num = array.index)
  	 
  	 event_numerics$event_created <- as.POSIXct(event_numerics$created/1000, origin = "1970-01-01")
  	 event_numerics$event_time <- as.POSIXct(event_numerics$time/1000, origin = "1970-01-01")
  	 event_numerics$event_updated <- as.POSIXct(event_numerics$updated/1000, origin = "1970-01-01")
  	 event_numerics$event_duration_minutes <- event_numerics$duration/60000

    group_id_events <- left_join(event_strings, event_numerics, by = c("rec_num" = "rec_num")) %>% 
      select(-duration, -created, -time, -updated, -duration)

    event_rating <- tbl_json %>% gather_array %>%
      # spread_values(event_id = jstring("id")) %>%
      enter_object("rating") %>% 
      my_spread_values(c("count","average"), jnumber) %>%
      select(-document.id, number_of_raters = count) %>%
      mutate(rec_num = array.index)

    event_group <- tbl_json %>% gather_array %>%
      # spread_values(event_id = jstring("id")) %>%
      enter_object("group") %>% 
      spread_values(
        group_created = jnumber("created"), 
        group_id = jnumber("id"), 
        group_join_mode = jstring("join_mode"), 
        group_name = jstring("name"), 
        group_urlname = jstring("urlname"), 
        group_member_name = jstring("who")
        ) %>% 
      select(-document.id) %>%
      mutate(group_organizing_event = group_id, rec_num = array.index)
    
      event_group$group_created <- as.POSIXct(event_group$group_created/1000, origin = "1970-01-01")
    
    group_id_events <- left_join( group_id_events, event_rating, by = c("rec_num" = "rec_num")) %>% 
      select(-array.index)
    group_id_events <- left_join( group_id_events, event_group, by = c("rec_num" = "rec_num")) %>% 
      select(-array.index, -rec_num)

      # accumulate batches into groups_id data frames
      if (offset == 0 ) {
        cum_group_id_events <- group_id_events
  	  } else {
        cum_group_id_events <- bind_rows(cum_group_id_events, group_id_events)
      }
    
      # get another batch or jump out of the retrieval loop
      offset <- offset + 1 
      if ( dim(event_strings)[1] < 200 ) { 
        # have run out of data for this group
        offset <-  -1
      } 
    
    Sys.sleep(1) # wait between iterations
    cat('.')
    }  
	
    cat("+")
    return(list("events" = cum_group_id_events))
  }  # finish this group_id

# test with:
# python_list <- get_event_data_frame(490808)
# data_groups_list <-  c("11038292", "16967362", "13789762")

get_many_groups <- function(list_of_ids){
  for (list_num in seq_along(list_of_ids) ) {
    # cat(paste(list_num, ",", list_of_ids[list_num], "\n") )
    dataframes_this_list <- get_event_data_frame(group_id = list_of_ids[list_num])
    # unpack the results
     # accumulate batches into groups_id data frames
      if (list_num == 1 ) {
        # initialize
        cum_events <- dataframes_this_list[["events"]]
  	    # cum_topics <- dataframes_this_list[["topics"]]
  	  } else {
  	    # accumulate
        cum_events <- bind_rows(cum_events, dataframes_this_list[["events"]])
        # cum_topics <- bind_rows(cum_topics, dataframes_this_list[["topics"]])
      }
    }
  return(list("all_events" = cum_events))  
  }

# data_groups_list <- c( "11038292","490808")
data_groups_list <- c("490808", "11038292", "16967362", "1685557", "18393607")
# data_groups_list <- c("11038292", "16967362", "13789762", "18393607", "15174102", "19149214", "17840052", "10136492", "6949282", "17836232", "6622532", "8245962", "490808","1685557")
many_groups <- get_many_groups(data_groups_list)

# more_data_groups_list <- c("19149214", "17753372","16786942")
# some_groups <- get_many_groups(more_data_groups_list)

# python <- get_many_groups("490808")

```
Extract and save
Odd that Python events don't turn up when in this query

```{r}
group_tags <- read_tsv("~/Documents/cch/tidymeetups/group_tags.tsv", col_types = "nc")
str(group_tags)

selected_events <- many_groups[["all_events"]]
# all_topics <- many_groups[["all_topics"]]

# all_members <- bind_rows(all_members,more_members)
# all_topics <- bind_rows(all_topics, more_topics)

selected_events <- left_join(selected_events,group_tags, by = c("group_organizing_event" = "ID"))

write_rds(selected_events, "selected_data_meetup_events.Rdata")
# write_rds(all_topics, "all_data_meetup_topics.Rdata")

str(selected_events)
```
retrieve
```{r}
all_members <- readRDS( "all_data_meetup_events.Rdata")
```
Inpsect and summarize
```{r}
upload_google_ss(all_events, "All Meetup events in the past 2 years - selected groups")
```
explore selected events 
```{r}
group_tags <- read_tsv("~/Documents/cch/tidymeetups/group_tags.tsv", col_types = "nc")
str(group_tags)
selected_events <- left_join(selected_events,group_tags, by = c("group_organizing_event" = "ID"))

selected_events  %>% filter(tag == "R Users" &  yes_rsvp_count < 5)  %>% select( event_time, name)
org_events <- selected_events %>% filter(!str_detect(name, "Coursera|MOOC"))

ggplot(data = org_events, aes(x = tag, y = yes_rsvp_count) ) + 
  geom_boxplot() + 
   ggtitle("Event size, selected meetups") +
  xlab("Group") +
  ylab("Interest measured by 'yes' RSVP's")

ggplot(org_events, aes(x = event_time, y = yes_rsvp_count, colour = tag) ) + geom_smooth(se = F) +
  geom_point() +
  ggtitle("Event size, selected meetups") +
  xlab("Date") +
  ylab("Interest measured by 'yes' RSVP's")

```
event frequency
```{r}
event_freq <- org_events %>% 
  arrange(tag, event_time) %>% 
  mutate( 
    last_event = lag(event_time,1, order_by = event_time),
    days_elapsed = round(as.numeric(event_time - last_event)/  86400)
    ) %>% 
  select(name, tag, last_event, event_time, days_elapsed)

ggplot(data = event_freq, aes(x = tag, y = days_elapsed) ) + 
  geom_boxplot() + 
   ggtitle("Event frequency, selected meetups") +
  xlab("Group") +
  ylab("Days since previous event")

```

