---
title: "Get Meetup data"
author: "John D. Smith"
date: "December 3, 2015"
output: html_document
---
&category=34,2

tech category=34
careerbiz - category=2

only=id,name
offset = 0-?

API docoumentation: http://www.meetup.com/meetup_api/docs/find/groups/ 
for testing: https://secure.meetup.com/meetup_api/console/?path=/find/groups

```{r}
library(httr)
library(lubridate)
library(jsonlite)
library(plyr)
library(dplyr)
library(tidyjson)
library(readr)
# library(rjson)
# library(RJSONIO)

options(stringsAsFactors = FALSE)

meetup_api <- Sys.getenv("meetup_api")
```
sample data documented here: http://www.meetup.com/meetup_api/docs/find/groups/
&only=created,category,description,id,join_mode,members,name,urlname,visibility,organizer,welcome_message,who,next_event
```{r Query API}
url_group_start <- paste0("https://api.meetup.com/find/groups?sign=true&photo-host=public&key=", meetup_api)
url_query <- "&zip=97206&radius=3&page=4"

page_num = 0
url_page <- paste0("&offset=", page_num)
# paste0(url_group_start,url_query,url_page)
url <- paste0(url_group_start,url_query,url_page)
url
raw_contents <- GET(url = url)
jsonp <- content(raw_contents, "text")
# prettify(jsonp[[1]]) # generates a huge amount of output!
# json <- gsub('([a-zA-Z_0-9\\.]*\\()|(\\);?$)', "", jsonp, perl = TRUE)
# json <- gsub('"','\"', jsonp, perl = T)
# tech_sample <- fromJSON(jsonp, flatten = T)
# tech_sample is a list of data frames?
# df  <- ldply(tech_sample, data.frame)

# show the first two records as JSON
tech_sample[1:2] %>% toJSON %>% prettify(indent = 2)

# raw_as_chars <- as.character(raw_contents$content)
# tech_sample <- fromJSON(url )

```
try tidyjson again!
```{r}
ts <- fromJSON(json)
ts1 <- ts[[1]]
dput(ts1, file = "ts1.txt")
df <- as.character(ts) %>% as.tbl_json %>% gather_array %>% 
  spread_values(visibility = jstring("visibility")) %>%
  enter_object(category) %>% 
  spread_values(
    category_name = jstring("name"),
    category_id = jstring("id")
  ) %>% select(who,name,category_name,category_id)
  
```

```{r}
df0 <- rbind.fill(lapply(tech_sample, as.data.frame))

page_num = 1
url_page <- paste0("&offset=", page_num)
tech_sample <- fromJSON(paste0(url_group_start,url_query,url_page) )
length(tech_sample)
df1 <- rbind.fill(lapply(tech_sample, as.data.frame))

df <- bind_rows(df0, df1)

df <- df %>% arrange(desc(members))
dfa1 <- dfa %>% select(-description)

# str(df)
```
create a data frame and examine

tech_decoded <- rawToChar(tech_sample$content)
# groups_list <- do.call(what = "rbind", args = lapply(tech_decoded, as.data.frame))
groups_list <- as.data.frame(fromJSON(tech_decoded, simplifyDataFrame = T, flatten = T))
groups_list <- flatten(groups_list, recursive = T)
groups_list <- ungroup(groups_list)
head(groups_list, n = 1)
typeof(groups_list)
groups_list <- as.data.frame(groups_list)
# write.csv(groups_list,path = "groups_list.csv" )
unl  <- unlist(groups_list)


```{r}
page_num = 0
url_page <- paste("&offset = ", page_num)
url_group_start <- paste0("https://api.meetup.com/find/groups?sign=true&photo-host=public&key=", meetup_api)
url_query <- "&zip=97206&radius=3&page=3"
all_sample <- GET(url = paste0(url_group_start,url_query,url_page))
all_sample$status_code
n_groups <- as.numeric(all_sample$headers$`x-total-count`)
n_groups

```
try to unpack the data frame
```{r}
tech_decoded <- tech_decoded %>% as.character %>% as.tbl_json()
tech_decoded %>% gather_array() %>% json_lengths()
df <- tech_decoded %>% gather_array() %>% gather_keys() %>% json_types() %>% as.data.frame()

typeof(df)

tech_decoded <- as.data.frame(tech_decoded)
tech_decoded %>% gather_array() %>% gather_keys()
typeof(tech_decoded)
```

```{r}
x <-  paste0('<hr><h2><a href="http://meetup.com/', df$urlname, '">', df$name, '</a></h2>for: <b>', df$members, "</b> ", df$who, 
            "<br>", 
            as.character(df$description), "</hr>")
x <- paste("<html>", x, "</html>")
writeLines(x, con = "all-meetups.html", sep = "\n")
```
?

